Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-09-25 paper/meg_exps.tex
a

We used the feature importance described in Algorithm \ref{algorithm:b2b_fi} to assess the extent to which each feature $X_i$ specifically improves the prediction of held-out $Y$ data, using a 5-fold cross-validation.

>>>>

We used the feature importance described in Algorithm \ref{algorithm:b2b_fi} to assess the extent to which each feature $X_i$ specifically improves the prediction of held-out $Y$ data, using a 5-fold cross-validation (with shuffled trials to homogeneize the distributions between the training and testing splits).
